Protecting Private Data in the Cloud: A Path Oblivious RAM Protocol

### 2014-11-22 paper/paper.tex
inserted all figures

% *** GRAPHICS RELATED PACKAGES ***
%
\ifCLASSINFOpdf
  % \usepackage[pdftex]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../pdf/}{../jpeg/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
\else
  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
  % will default to the driver specified in the system graphics.cfg if no
  % driver is specified.
  % \usepackage[dvips]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../eps/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.eps}
\fi
% graphicx was written by David Carlisle and Sebastian Rahtz. It is
% required if you want graphics, photos, etc. graphicx.sty is already
% installed on most LaTeX systems. The latest version and documentation can
% be obtained at: 
% http://www.ctan.org/tex-archive/macros/latex/required/graphics/
% Another good source of documentation is "Using Imported Graphics in
% LaTeX2e" by Keith Reckdahl which can be found as epslatex.ps or
% epslatex.pdf at: http://www.ctan.org/tex-archive/info/
%
% latex, and pdflatex in dvi mode, support graphics in encapsulated
% postscript (.eps) format. pdflatex in pdf mode supports graphics
% in .pdf, .jpeg, .png and .mps (metapost) formats. Users should ensure
% that all non-photo figures use a vector format (.eps, .pdf, .mps) and
% not a bitmapped formats (.jpeg, .png). IEEE frowns on bitmapped formats
% which can result in "jaggedy"/blurry rendering of lines and letters as
% well as large increases in file sizes.
%
% You can find documentation about the pdfTeX application at:
% http://www.tug.org/applications/pdftex

@@

% author names and affiliations
% use a multiple column layout for up to three different
% affiliations
\author{\IEEEauthorblockN{Ethan Zou}
\IEEEauthorblockA{Lexington High School\\ Lexington, MA \\
Email: zouethan19@gmail.com}
\and
\IEEEauthorblockN{Nathan Wolfe}
\IEEEauthorblockA{The Roxbury Latin School\\ Roxbury, MA\\
Email: nathanwolferl@gmail.com}}

@@

diagram

@@

image

@@

Dropbox’s baseline functions allow users to read and write files to a remote server in the cloud. Thus, we needed a way for our ORAM system to support the reading and writing of files of various sizes. Our solution was implementing the User File System, which enables the writing of files of different sizes.

@@

image

@@

graph

\subsection{Optimal Segment Size}
graph

@@

\subsection{Initial ORAM Efficiency}
graph

@@

\subsection{Multi-Block Fetching}
graph

@@

\subsection{Block Packing}
two graphs

@@

\subsection{Dynamic Growing and Shrinking}
graph

>>>>

% *** GRAPHICS RELATED PACKAGES ***
%
\ifCLASSINFOpdf
\usepackage[pdftex]{graphicx}
  % declare the path(s) where your graphic files are
\graphicspath{ {gfx/} }
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
\DeclareGraphicsExtensions{.pdf,.jpeg,.png}
\else
  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
  % will default to the driver specified in the system graphics.cfg if no
  % driver is specified.
  % \usepackage[dvips]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../eps/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.eps}
\fi
% graphicx was written by David Carlisle and Sebastian Rahtz. It is
% required if you want graphics, photos, etc. graphicx.sty is already
% installed on most LaTeX systems. The latest version and documentation can
% be obtained at: 
% http://www.ctan.org/tex-archive/macros/latex/required/graphics/
% Another good source of documentation is "Using Imported Graphics in
% LaTeX2e" by Keith Reckdahl which can be found as epslatex.ps or
% epslatex.pdf at: http://www.ctan.org/tex-archive/info/
%
% latex, and pdflatex in dvi mode, support graphics in encapsulated
% postscript (.eps) format. pdflatex in pdf mode supports graphics
% in .pdf, .jpeg, .png and .mps (metapost) formats. Users should ensure
% that all non-photo figures use a vector format (.eps, .pdf, .mps) and
% not a bitmapped formats (.jpeg, .png). IEEE frowns on bitmapped formats
% which can result in "jaggedy"/blurry rendering of lines and letters as
% well as large increases in file sizes.
%
% You can find documentation about the pdfTeX application at:
% http://www.tug.org/applications/pdftex

@@

% author names and affiliations
% use a multiple column layout for up to three different
% affiliations
\author{\IEEEauthorblockN{Ethan Zou}
\IEEEauthorblockA{Lexington High School\\ Lexington, MA \\
Email: zouethan19@gmail.com}
\and
\IEEEauthorblockN{Nathan Wolfe}
\IEEEauthorblockA{The Roxbury Latin School\\ West Roxbury, MA\\
Email: nathanwolferl@gmail.com}}

@@

\begin{center}
\noindent\includegraphics[width=6cm]{220.png}
\end{center}

@@

\begin{center}
\noindent\includegraphics[width=8.5cm]{310.png}
\end{center}

@@

Dropbox's baseline functions allow users to read and write files to a remote server in the cloud. Thus, we needed a way for our ORAM system to support the reading and writing of files of various sizes. Our solution was implementing the User File System, which enables the writing of files of different sizes.

@@

\begin{center}
\noindent\includegraphics[width=8cm]{320.png}
\end{center}

@@

\begin{center}
\noindent\includegraphics[width=8.5cm]{510.png}
\end{center}

\subsection{Optimal Segment Size}
\begin{center}
\noindent\includegraphics[width=8.5cm]{520.png}
\end{center}

@@

\subsection{Initial ORAM Efficiency}
\begin{center}
\noindent\begin{tabular}{ l c r}
  \bf{Disk} & \bf{Disk + Encryption} & \bf{Disk + ORAM} \\
  42.13 & 24.42 & 0.66 \\
\end{tabular}
\end{center}

@@

\subsection{Multi-Block Fetching}
\begin{center}
\noindent\includegraphics[width=8.5cm]{540.png}
\end{center}

@@

\subsection{Block Packing}
\begin{center}
\noindent\includegraphics[width=4.25cm]{550.png}\includegraphics[width=4.25cm]{551.png}
\end{center}

@@

\subsection{Dynamic Growing and Shrinking}
\begin{center}
\noindent\includegraphics[width=8.5cm]{560.png}
\end{center}
